### 2019-12-17 tex/ms.tex
minor edits

For this throughput study, we use a set of 22 GFA exposures taken on 20191025. The exposures have 21338 $\le$ EXPID $\le$ 21360, with EXPID = 21350 omitted because of its short 1 second exposure time. The program name (PROGRAM keyword header parameter) of this set of exposures is ``dense fields''. These exposures are all centered in the vicinity of (RA, Dec) =  (80$^{\circ}$, 30$^{\circ}$), which is near the Galactic anticenter at ($l_{gal}$, $b_{gal}$) $\approx$ (176, $-4$). These exposures were chosen for the following reasons:

\begin{itemize}
\item They were taken during a photometric time period.
\item They were taken in reasonably good seeing. The median FWHM is 0.98$''$ (min = 0.94$''$, max = 1.49$''$, dispersion = 0.12$''$).
\item They are taken in a region of high source density. This provides more sources per exposure to compare against PS1, better assurance of successful astrometric calibration, and also enables high-quality PSF modeling. 
\item They are relatively long GFA exposures (the unique exposure times are 30 seconds and 60 seconds), further improving the density of well-detected sources.
\item The airmass is very nearly 1, minimizing the impact of any inaccuracies in the atmospheric transmission component of GFA throughput prediction.
\item All six cameras worth of guide GFA images are available for all exposures in this sequence.
\item The exposures were dithered at a scale of $\sim$30$''$ per coordinate, so that we are not always sampling the same stars at the same GFA pixel locations during every single exposure.
\end{itemize}

>>>>

For this throughput study, we use a set of 22 GFA exposures taken on 20191025. The exposures have 21338 $\le$ EXPID $\le$ 21360, with EXPID = 21350 omitted because of its short 1 second exposure time. The program name (PROGRAM keyword header parameter) of this set of exposures is ``dense fields''. These exposures are all centered in the vicinity of (RA, Dec) =  (80$^{\circ}$, 30$^{\circ}$), which is near the Galactic anticenter at ($l_{gal}$, $b_{gal}$) $\approx$ ($176^{\circ}$, $-4^{\circ}$). These exposures were chosen for the following reasons:

\begin{itemize}
\item They were taken during a photometric time period.
\item They were taken in reasonably good seeing. The median FWHM is 0.98$''$ (min = 0.94$''$, max = 1.49$''$, dispersion = 0.12$''$).
\item They were taken in a region of high source density. This provides more sources per exposure to compare against PS1, better assurance of successful astrometric calibration, and also enables high-quality PSF modeling. 
\item They are relatively long GFA exposures (the unique exposure times are 30 seconds and 60 seconds), further improving the density of well-detected sources.
\item The airmass is very nearly 1, minimizing the impact of any inaccuracies in the atmospheric transmission component of GFA throughput prediction.
\item All six cameras worth of guide GFA images are available for all exposures in this sequence.
\item The exposures were dithered at a scale of $\sim$30$''$ per coordinate, so that we are not always sampling the same stars at the same GFA pixel locations during every single exposure.
\end{itemize}
